\chapter*{Acknowledgments}



\epigraph{
    To be blunt, this exercise is the equivalent of fishing in the dark, 
    with a blindfold on, with a net of an arbitrary size, 
in an ocean trying to not catch fish, but something else 
that may or may not look like fish that might or might not be in the ocean.}{\textit{Sakarias Frette | Spring 2023}}

This thesis has been a rollercoaster of a project, with its ups and downs, periods of yoy and of mild clinical depression.
Never the less, it is finally done, my master project. It, like so much in my life could not have been done without help. 
First of all, thanks to the No Carbs Company for creating the most delicous and addictive energy drink, the NOCCO. They have 
served my lymbic system well and kept my need for caffeine somewhat at bay. I would also thank Bunnpris at Frederikkes plass 
for selling them for as long as you did, all though I have to pick a bone with you guys about the somewhat axiomatically 
wrong choice to stop selling them. On the other hand, I enjoyed your warm burgers as well, I guess that makes a bit up for it. \par 
Throughout my education here at the Univesity of Oslo, I have had the pleasure of working with, befriending, 
and working out with several funny, smart, and close friends. William Hirst, Samir Noor, Anders Vestengen and 
Mikkel Metzch Jensen, you have all given me five excellent years with a lot of fun. Through difficult exams, long days, deadlines, 
heavy workouts, fun parties, UFC, Formula 1, movie nights and much much more we have made some beautiful bonds of friendship 
that I will sherish for ever. This is just the beginning. \par 
To my mum and dad, Live Cecilie and Jarle Vidar. You have guided me through thick and thin with your excellent guidance and wisdom. 
You are what every parents should aspire to be. Loving, just, caring, strict but fair, full of insight and interests for your 
different offspring. I know I am not always easy to deal with, but you have done right by me for the last 25 years, and I am 
forever grateful. Dad, your longstanding fascination and curiosity of nature  is admirable. Your ability to keep a cool head is envious, 
and you are very, very funny. You saw a potential within me to pursue the natural sciences. You have always been helpful and supportive 
with good advice. Thank you for this. Mum, your love knows no bounduries. You have children all over the world, as you should, 
for it is selfish of us to not share your heart with others. Where the natural sciences have been dad's department, the ways 
of the heart and soul have been yours. You are what I aspire to be in matters of the heart and soul. This I know for a fact. 
Thank you both for my upbringing and for the parents you are to me. I am forever in your debt. \par 
To Ern. My lovely girlfriend, training partner and tickle monster. You are inspiring, with your hard work ethic, your ambition 
and your drive. I would not have thought in October how much time we would spend together, how much fun we have had, and how happy 
I would be. You keep me on my toes, you push me when I need it, and hugs me when I need it. Truly you are one of a kind. 
And all though I tend to make a face when you bite me, and it hurts a bit, I do actually like it $;)$. Sometimes. Love you boo.\par
Finally, to Professor Farid Ould-Saada, Dr. Eirik Gramstad and Dr. James Catmore. Thank you for an exiting and difficult proejct. 
It is funny to look back to the first weeks of my masters program and remenice about how little I actually knew about physics, 
the porocess of science research, machine learning applications and much much more. These past two years have been an education 
to say the least. The tools I bring with me are credited to you. Thanks for being patient with me, as I know I had a lot of questions. 
the weekly meetings, the questionairs and bugfixing are just some of the many moments I look back fondly on, and will bring with me. 
My hope is that my work will help the next masters students. If not then I hope you at least had some fun and interesting talks 
and discoveries with me. Until we meet again. 
