\section{ROOT}
ROOT is an open-source data analysis framework used in high energy physics. It can do fast data manipulation, save and access data, 
create graphics for publication, and even combine with high level languanges such as R and Python.


\subsection*{RDataFrame}
RDataFrame's main purpose is to make reading and handling of ROOT files easier, especially in 
relation to modern machine learning tools and their respective frameworks and environments. 
This is done by creating a dataframe type of structure of the ROOT n-tuples, and then 
lazily\footnote{In this context lazily means that the functions and or cuts are done first after 
all have been registered, see \href{https://root.cern/doc/master/classROOT_1_1RDataFrame.html}{ROOT 
guidelines} for more.} apply contraints to the data. Using PyROOT
\footnote{\href{https://root.cern/manual/python/}{PyROOT website}}, RDataFrame can be accessed in 
Python, as the functionality is wrapped around a C++ class. Below is a code example of how
to create a RDataFrame object, apply a cut and then create a column for later use. Here, good 
leptons are defined first, denoted as "ele\_SG" and "muo\_SG". A cut is then applied where we 
require that the number of good leptons is always 3\footnote{Final states with two leptons present wre also analysed}. 
Finally, a column is created where the 
combination of type of leptons in the 3 lepton system is stored, as well as creating a histogram 
containing the results for that given channel\footnote{A channel here refers to a certain decay 
channel. The simulations of the SM is divided into several channels, and some look more alike than others. One example is 
the Higgs decay channel, with possible decays such as two photons, W bosons or Z bosons. This pertains 
to simulated events only, as we cannot control what decay channels we get in the data recorded at ATLAS} 
k. Notice here that if the variable already exists as a column in the dataframe, arithmetic and logic 
can be applied directly using those columns to create new one. More complicated variables, such as 
the flavor combination for the leptons, or the invariant mass of two particles must be found or 
calculated using C++ functions. An example of such a C++ function is shown in code example \ref{code:python_func_example}.

\begin{figure}[h!]
    \centering
\begin{lstlisting}[language=Python, style=pythonstyle, label={code:python_func_example}]
import ROOT as R

R.EnableImplicitMT(200) # Enable multithreading, sets number of threads to 200 or the highest number possible if the number of threads is less than 200     
R.gROOT.ProcessLine(".L helperFunctions.cxx+") # Load the C++ helper functions in ROOT interpreter
R.gSystem.AddDynamicPath(str(dynamic_path)) # Add the path to the library with the helper functions to the ROOT interpreter
R.gInterpreter.Declare(
    '#include "helperFunctions.h"'
)  # Header with all helper functions
R.gSystem.Load("helperFunctions_cxx.so")  # Library with the myFilter function

df_mc = getDataFrames(mypath_mc) # Function to create a dictionary of RDataFrames for each channel in the SM MC and possible signal samples
df_data = getDataFrames(mypath_data) # Function to create a dictionary of RDataFrames for ATLAS data
df = {**df_mc, **df_data} # Combine the two dictionaries



for k in df.keys(): #* Loop over all channels, i.e [Zeejets, ttbar, data15, ...]

    # Define "good" electrons
    df[k] = df[k].Define(
        "ele_SG",
        "ele_BL && lepIsoLoose_VarRad && lepTight && (lepD0Sig <= 5 && lepD0Sig >= -5)",
    ) 
    # Define "good" muons 
    df[k] = df[k].Define(
        "muo_SG",
        "muo_BL && lepIsoLoose_VarRad && (lepD0Sig <= 3 && lepD0Sig >= -3)",
    )  
    # Define "good" leptons based on good electrons and muons
    df[k] = df[k].Define("isGoodLep", "ele_SG || muo_SG")

    #* Number of good leptons
    df[k] = df[k].Define(
                "nlep_SG", "ROOT::VecOps::Sum(ele_SG)+ROOT::VecOps::Sum(muo_SG)"
            )

    #* Require exactly 3 good leptons
    df[k] = df[k].Filter("nlep_SG == 3", "3 SG leptons")

    #* Define flavor combination based on leptons available
    df[k] = df[k].Define("flcomp", "flavourComp3L(lepFlavor[ele_SG || muo_SG])")

    #* Histogram with the flavor combinations
    histo[f"flcomp_{k}" ] = df[k].Histo1D(
        (
            f"h_flcomp_{k}",
            f"h_flcomp_{k}",
            len(fldic.keys()),
            0,
            len(fldic.keys()),
        ),
        "flcomp",
        "wgt_SG",
    )
    \end{lstlisting}
    \caption[RDataFrame code example]{Example of event selection done using RDataFrame. Four example features are created here, the "good electrons", "good muons",
    "good leptons" and flavor combination of leptons. Then a filter is applied to the RDataFrame structure, and finally a histogram is created. In section \ref{sec:algo_impl}
    it is shown how to implement the Rapidity-Mass matrix from section \ref{sec:rmm} in event selection.}
    \label{code:rdata}
\end{figure}

In the code example \ref{code:python_func_example} we see how RDataframe can be used for event selection. Line 1-9 are settings for ROOT, 
number of threads to use in the paralellization, extra helper functions written in C++ with .h and .so files and the path to the folder.
Lines 11-13 create a dictionary containing the ROOT RDataFrames used for event selection. These are categorized by channel name. 
The loop on line 15 does event selection for each channel sample, defining new variables in the RDataFrame, applying filters and creating histograms.
Some variables are constructed using variables already in the ROOT files such as energy and mass. Through custom C++ functions
these properties can be added to the RDataFrames. Code example \ref{code:cpp_func_example} shows a custom C++ function which is used in work of this thesis.

\begin{figure}[h!]
    \centering
\begin{lstlisting}[language=C++, style=cppstyle, label={code:cpp_func_example}]
double getM(VecF_t &pt_i, VecF_t &eta_i, VecF_t &phi_i, VecF_t &e_i,
            VecF_t &pt_j, VecF_t &eta_j, VecF_t &phi_j, VecF_t &e_j,
            int i, int j)
{
    /* 
    Calculates the invariant mass between two particles.
    If the particles are not found, or the index is out of range,
    function returns zero, else returns the invariant mass.
    */

    const auto size_i = int(pt_i.size());
    const auto size_j = int(pt_j.size());

    if (size_i == 0 || size_j == 0){return 0.;}
    if (i > size_i-1){return 0.;}
    if (j > size_j-1){return 0.;}

    TLorentzVector p1;
    TLorentzVector p2;

    p1.SetPtEtaPhiM(pt_i[i], eta_i[i], phi_i[i], e_i[i]);
    p2.SetPtEtaPhiM(pt_j[j], eta_j[j], phi_j[j], e_j[j]);

    double inv_mass = (p1 + p2).M();

    return inv_mass;
}
\end{lstlisting}
\caption[C++ function example]{Example of a C++ function used in event selection. This function is used to calculate the invariant mass between two particles.
It takes the kinetic parameters for both particles and the index for which of the leptons available to compute for. If the particles do not exit for that event, it returns zero.  }
\end{figure}
This C++ function creates Lorentz vectors for two particles, and then returns the invariant mass based on the parameters sent in. 
This function will be used on all the leptons in a given event. If one particle or both do not exist, the C++ function will
return zero as the invariant mass\footnote{The invariant mass function getM is used for jet-jet, jet-lepton and lepton-lepton invariant masses}. \par


\begin{figure}[h!]
    \centering
\begin{lstlisting}[language=Python, style=pythonstyle, label={code:python_func_example_2}]
import pandas as pd 

def Convert_RDF_to_numpy(df, PATH_TO_STORE):


    cols = df.keys()

    for k in cols:

        print(f"Transforming {k}.ROOT to numpy")
        numpy = df[k].AsNumpy(DATAFRAME_COLS) #* DATAFRAME_COLS is a list of columns to be converted to a numpy array
        print(f"Numpy conversion done for {k}.ROOT")
        df1 = pd.DataFrame(data=numpy) #* Convert to pandas dataframe
        print(f"Transformation done")
        
        #* Convert to HDF5
        df1.to_hdf(
            PATH_TO_STORE + f"/{k}_3lep_df_forML_bkg_signal_fromRDF.hdf5", "mini"
        )

        #* Flush memory for new dataframe
        df1 = pd.DataFrame()

\end{lstlisting}
\caption[Conversion from RDataFrame to NumPy]{Loop converting RDataFrames to NumPy structures, before being stored as HDF5 files.
Her $df[k]$ is a dictionary containing each channel, with channel name as key.}
\end{figure}

Once the event selection is done, the features have been chosen and histograms have been 
drawn, the RdataFrame can be converted to a Pandas dataframe. This is a very popular 
choice for data structure when performing data analysis in python. This is done through an 
intermediate step of converting the RDataframe to a numpy filestructure, which then can 
be converted to a Pandas\cite{reback2020pandas} dataframe or some other framework.
The new Pandas dataframes are stored as HDF5\cite{hdf5} files to be used later. This is 
because the HDF5 format has a very good compression ratio, and is very fast to read and write. 