\section{BSM model physics}

\subsection*{Heavy neutrinos}
Parity symmetry is suggested to be restored at high energies by the introduction of 
a right handed weak symmetry, leading to right handed weak charged bosons, $W_R^{'\pm}$. 
These mediators, as with the rest, decays faster than the detection ability at the LHC\footnote{Large Hadron Collider at CERN}, thus 
evidence of such a boson would come from the detection of the decay of a heavy neutrino. Heavy neutrinos can 
be produced in proton proton collisions through either the right handed $W_R^{'\pm}$ bosons or
the SM $W^{\pm}$ bosons, under given conditions.


\begin{figure}[h!]
    \centering
    \caption[Heavy neutrino signal diagram, SM W]{Proton-proton collision with heavy neutrino production via SM $W^{\pm}$ boson into 3 lepton final state. Read the graph from left to right.}
\begin{tikzpicture}
    \begin{feynman}
    
        \vertex at (0.5, 1.) (a2){\(q\)} ;
        \vertex at (0.5, -1.)  (a5){\(\bar{q}'\)} ;

        \vertex at (1.5, 0.0) (c);
        \vertex at (3., 0.0) (d);

        \vertex at (5.5, 1.) (f1) {\(l^{\pm}\)} ;
        \vertex at (3.8,-0.88) (f2) {\(N\)};

        \vertex at (5.5, -0.2) (f3) {\(l\)} ;

        \vertex at (5, -1.7) (e)  ;

        \vertex at (6, -1.0) (f4) {\(l\)} ;
        \vertex at (6, -2.2) (f5) {\(\nu\)} ;

        
    \diagram*{


        (a2) -- [fermion] (c) -- [boson] (d),
    
        (a5) -- [anti fermion] (c) -- [boson, edge label = {$W^{(*)\pm}$}] (d),
        (d) -- [fermion] (f1),
        (d) -- [fermion] (f2),
        (f2) -- [fermion] (f3),
        (f2) -- [boson, edge label = {$W^{(*)}$}] (e),
        (e) -- [fermion] (f4),
        (e) -- [fermion] (f5),
        ;
    };
    \end{feynman}
    \end{tikzpicture}
    \label{fig:Target_model_1}
    
\end{figure}



\begin{figure}[h!]
    \centering
    \caption[Heavy neutrino signal diagram, right handed W]{Proton-proton collision with heavy neutrino production via right-handed $W_R^{\pm}$ boson into 3 lepton final state. Read the graph from left to right.}

\begin{tikzpicture}
    \begin{feynman}
    
        \vertex at (0.5, 1.) (a2){\(q\)} ;
        \vertex at (0.5, -1.)  (a5){\(\bar{q}'\)} ;

        \vertex at (1.5, 0.0) (c);
        \vertex at (3., 0.0) (d);

        \vertex at (5.5, 1.) (f1) {\(l^{\pm}\)} ;
        \vertex at (3.8,-0.88) (f2) {\(N\)};

        \vertex at (5.5, -0.2) (f3) {\(l\)} ;

        \vertex at (5, -1.7) (e)  ;

        \vertex at (6, -1.0) (f4) {\(l\)} ;
        \vertex at (6, -2.2) (f5) {\(\nu\)} ;

        
    \diagram*{


        (a2) -- [fermion] (c) -- [boson] (d),
    
        (a5) -- [anti fermion] (c) -- [boson, edge label = {$W_R^{'\pm}$}] (d),
        (d) -- [fermion] (f1),
        (d) -- [fermion] (f2),
        (f2) -- [fermion] (f3),
        (f2) -- [boson, edge label = {$W_R^{'(*)}$}] (e),
        (e) -- [fermion] (f4),
        (e) -- [fermion] (f5),
        ;
    };
    \end{feynman}
    \end{tikzpicture}
    \label{fig:Target_model_2}
    \end{figure}

Note that the right most $W$ and $W_R$ bosons have an asterix as a superfix. This is because 
the bosons can be virtual. This means that if the mass of the heavy neutrino is less than the W boson,
it cannot produce it, but it can produce a virtual one such that the decay still happens. 

\subsection*{Supersymmetry}
Supersymmetry is another BSM theory that attempts to solve two other problems that the standard model has. 
First, the hierarchy problem . As the standard model is a perturbative theory, the Higgs mass increases at 
higher energies. The problem is that when you approach higher and higher energies, this mass goes to infinity, 
which is not physical. Supersymmetry solves this problem. The theory introduces a supersymmetric partner to each particle
in the standard model. The result is that the contributions to the Higgs mass from fermions and bosons mainly cancel, 
thus fixing the hierarchy problem. Another problem we have with the standard model
is that is does not have a field for for dark matter. Some supersymmetry models have a dark matter candidate, 
thus the Supersymmetry search is quite large at CERN. 